\chapter{Abstract}


Software developers interact with integrated development environments (IDEs) by issuing commands that execute various programming tools, from source code formatters to build tools. Several studies has shown that despite the usefulness of provided tools and capabilities to perform tasks such as: navigating among classes and methods, continuous compilation, code refactoring and integrated debugging, IDEs usually tend to overload developers resulting a chaotic state. In other words, commonly developers spend time shifting between several artifacts of the working environment in order to reach their goal, and this repeated process increases the complexity of identifying the relevant information to solve their assignment. 

For this reason, an assortment of usage metrics plugins to gather developers' activity have been developed in an attempt to understand a developers' workflow. Understanding the workflow, as well as the skillset and experience of a developer is the first step into improving their productivity and reducing the unneccessary complexity created within IDEs. 

In this work, we analyze and provide an overview of the project itself and discuss concepts involved: by uncovering available existing plugins for recording a developer's interaction within an IDE. Further, we describe in detail the software tool which was selected for expansion and features which were developed to allow capture, mine and analyses for the process of software development. Finally, we present the results of mining deelopers' interactions according to their IDE usage.

We aim to contribute information for modelling an automatic activity detection tool capable of tracking the workflow of developers’ activity which potentially will be used as input in later studies for a reconfiguration program supporting the developer.


% \todo{write}
%we also examine the link between programmer's interaction and some of the contextual factors of software development
%In this work, i'd like to propose a model to present the user interactions I gather from the IDE. in parallel with the process mining we gonna make


 % we explore how the basic characteristics of software maintenance task structures can be better understood, how latent dependence between program artifacts can be detected at interaction time, and show how patterns of interaction coupling can be identified. 

 % We also examine the link between programmer interactions and some of the contextual factors of software development, such as the nature of the task being performed, the design of the software system, and the expertise of the developers. In particular, we explore how task boundaries can be automatically detected from interaction histories, how system design and developer expertise may affect interaction coupling, and whether newcomer and ex- pert developers differ in their interaction history patterns. These findings can help us to better reason about the multidimensional nature of software development, to detect po- tential problems concerning task, design, expertise, and other contextual factors, and to build smarter tools that exploit the inherent patterns within programmer interactions and provide improved support for task-aware and expertise-aware software development.