\begin{thebibliography}{10}
\bibitem{c1} 
Jeroen Ploeg, Dipan P. Shukla, Nathan van de Wouw, and Henk Nijmeijer, fellow, IEEE
\textit{Controller Synthesis for String Stability of Vehicle Platoons}, IEEE Trans. Veh. Int. Transp. , April 2014


\bibitem{c2}
Vicente Milanes, Steven E. Shladover, John Spring, Christopher Nowakowski, Hiroshi Kawazoe, and Masahide Nakamura
\textit{Cooperative Adaptive Cruise Control in Real Traffic Situations},  IEEE Trans. Veh. Int. Transp., February 2014

\bibitem{c4}
Mario di Bernardo, Fellow, IEEE, Alessandro Salvi, Student Member, IEEE, and Stefania Santini, member IEEE
\textit{Distributed Consensus Strategy for platooning of vehicles in the presence of time varying heterogenous communication Delays},IEEE Trans. Veh. Int. Transp., February 2015

\bibitem{c5}
Zhe Liu, Weidong Chen, Member, IEEE, Junguo Lu, Hesheng Wang, Senior Member, IEEE and Jingchuan Wang
\textit{Formation Control of Mobile Robots Using Distributed Controller With Sampled Data and Communication Delays}, IEEE Trans. Control System Technology , April 2016

\bibitem{ec5}
Dong Sun,  Senior Member, IEE, Can Wang, Wen Shang, and Gang Feng, Fellow, IEEE
\textit{Leader–Follower Formation and Tracking Controlof Mobile Robots Along Straight Paths}, IEEE Trans. on Robotics, October 2009


\bibitem{c6}
Kristoffer Lidstrom, Member IEEE, Katrin Sjoberg, Ulf Holmberg, Johan Andersson, Fredrik Bergh, Mattias Bjade, and Spencer Mak
\textit{A modular CACC System Integration and Design}, IEEE Trans. Veh. Int. Transp. , April 2012

\bibitem{fc1}
Antonio Loria, Janset Dasdemir, and Nohemi Alvarez Jarquin
\textit{Leader–Follower Formation and Tracking Controlof Mobile Robots Along Straight Paths}, IEEE Trans. Control System Technology , March 2016

\bibitem{wp1}
Jeroen Ploeg, Nathan van de Wouw, and Henk Nijmeijer, Fellow, IEEE
\textit{Lp String Stability of Cascaded Systems: Application to Vehicle Platooning}


\bibitem{p1}
Valerio Turri, Bart Besselink, and Karl H. Johansson, Fellow, IEEE
\textit{Cooperative Look-Ahead Control for Fuel-Efficient
and Safe Heavy-Duty Vehicle Platooning}, January 2017
\bibitem{p4}
Jeffrey Larson, Kuo-Yun Liang, and Karl H. Johansson, Fellow, IEEE
\textit{A Distributed Framework for Coordinated
Heavy-Duty Vehicle Platooning}, February 2015


\bibitem{n1}
Jeroen Ploeg, Bart T. M. Scheepers, Ellen van Nunen, Nathan van de Wouw, Henk Nijmeijer
\textit{Design and Experimental Evaluation of Cooperative Adaptive Cruise Control}, IEEE Trans. Veh. Int. Transp. Sys. , October 2011



\end{thebibliography}